---
title: "Analysis report"
author: "Paulo Czarnewski"
date: "`r Sys.Date()`"
output:
  html_document:
    fig_caption: yes
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: no
  pdf_document:
    toc: yes
---

<style type="text/css">
.main-container {
  max-width: 1800px;
  margin-left: auto;
  margin-right: auto;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F,results = 'hide',fig.width=10)
```


# Report {.tabset}

## Quality control {.tabset}

### Gene QC
##### Gene Biotype proportions

Here we investigated the proportion of different gene biotypes encountered in the dataset.

```{r,results='asis', echo=FALSE, fig.width=10}
files <- "/Users/paulo.barenco/Desktop/Desktop_stuff/MyProject/embryonic/analysis/1_qc/Gene_biotype_proportions.png"
for (i in files){ cat("![](",i,")") }
```
**Figure.**Proportion of gene biotypes in the dataset.

##### Gene Family proportion

Here we investigated the proportion of different gene families encountered in the dataset, either before of after filtering.

```{r,results='asis', echo=FALSE, fig.width=10}
files <- "/Users/paulo.barenco/Desktop/Desktop_stuff/MyProject/embryonic/analysis/1_qc/Gene_familty proportions.png"
for (i in files){ cat("![](",i,")") }
```
**Figure.**Proportion of gene biotypes in the dataset.


### QC plots BEFORE filtering
```{r,results='asis', echo=FALSE, fig.width=10}
files <- c("/Users/paulo.barenco/Desktop/Desktop_stuff/MyProject/embryonic/analysis/1_qc/QC_dataset.png",
           "/Users/paulo.barenco/Desktop/Desktop_stuff/MyProject/embryonic/analysis/1_qc/QC_embryonic_age.png",
           "/Users/paulo.barenco/Desktop/Desktop_stuff/MyProject/embryonic/analysis/1_qc/QC_genotype.png",
           "/Users/paulo.barenco/Desktop/Desktop_stuff/MyProject/embryonic/analysis/1_qc/QC_sex.png")
for (i in files){ cat("![](",i,")") }
```


### QC plots AFTER filtering
```{r,results='asis', echo=FALSE, fig.width=10}
files <- c("/Users/paulo.barenco/Desktop/Desktop_stuff/MyProject/embryonic/analysis/1_qc/QC_dataset_FILTERED.png",
           "/Users/paulo.barenco/Desktop/Desktop_stuff/MyProject/embryonic/analysis/1_qc/QC_embryonic_age_FILTERED.png",
           "/Users/paulo.barenco/Desktop/Desktop_stuff/MyProject/embryonic/analysis/1_qc/QC_genotype_FILTERED.png",
           "/Users/paulo.barenco/Desktop/Desktop_stuff/MyProject/embryonic/analysis/1_qc/QC_sex_FILTERED.png")
for (i in files){ cat("![](",i,")") }
```


## Dimensionalty reduction {.tabset}


### UMAP

#### Metadata (continuous)
```{r}
files <- "/Users/paulo.barenco/Desktop/Desktop_stuff/MyProject/embryonic/analysis/2_clustering/UMAP_plots/umap_metadata_dim1_dim2.png"
for (i in files){ cat("![](",i,")") }
```

#### Metadata (factors)
```{r, results='asis', echo=FALSE, fig.width=5}
files <- "/Users/paulo.barenco/Desktop/Desktop_stuff/MyProject/embryonic/analysis/2_clustering/UMAP_plots/umap_metadata_factors_dim1_dim2.png"
for (i in files){ cat("![](",i,")") }
```


### PCA

#### Percentage explained variance
```{r, results='asis', echo=FALSE}
files <- c("/Users/paulo.barenco/Desktop/Desktop_stuff/MyProject/embryonic/analysis/2_clustering/PCA_plots/Varianc_explained_PC.png")
for (i in files){ cat("![](",i,"){width=33%}") }
for (i in files){ cat("![](",i,"){width=33%}") }
for (i in files){ cat("![](",i,"){width=33%}") }
```


#### Genes that impact the most onto PCs
```{r, results='asis', echo=FALSE}
files <- c("/Users/paulo.barenco/Desktop/Desktop_stuff/MyProject/embryonic/analysis/2_clustering/PCA_plots/Varianc_explained_PC.png")
for (i in files){ cat("![](",i,")") }
```


#### PCA plot per Metadata (continuous)
```{r, results='asis', echo=FALSE}
files <- c("/Users/paulo.barenco/Desktop/Desktop_stuff/MyProject/embryonic/analysis/2_clustering/PCA_plots/pca_metadata_dim1_dim2.png","/Users/paulo.barenco/Desktop/Desktop_stuff/MyProject/embryonic/analysis/2_clustering/PCA_plots/pca_metadata_dim3_dim4.png")
for (i in files){ cat("![](",i,")") }
```


#### PCA plot per Metadata (continuous)
```{r, results='asis', echo=FALSE}
files <- c("/Users/paulo.barenco/Desktop/Desktop_stuff/MyProject/embryonic/analysis/2_clustering/PCA_plots/pca_metadata_dim1_dim2.png","/Users/paulo.barenco/Desktop/Desktop_stuff/MyProject/embryonic/analysis/2_clustering/PCA_plots/pca_metadata_dim3_dim4.png")
for (i in files){ cat("![](",i,")") }
```


#### Metadata (factors)
```{r, results='asis', echo=FALSE}
files <- c("/Users/paulo.barenco/Desktop/Desktop_stuff/MyProject/embryonic/analysis/2_clustering/PCA_plots/pca_metadata_factors_dim1_dim2.png","/Users/paulo.barenco/Desktop/Desktop_stuff/MyProject/embryonic/analysis/2_clustering/PCA_plots/pca_metadata_dim3_dim4.png")
for (i in files){ cat("![](",i,")") }
```


### Clustering {.tabset}

#### HC

```{r, results='asis', echo=FALSE}
files <- c("/Users/paulo.barenco/Desktop/Desktop_stuff/MyProject/embryonic/analysis/2_clustering/clustering/clustering_HC_umap.png")
for (i in files){ cat("![](",i,")") }
```


#### kmeans

```{r, results='asis', echo=FALSE}
files <- c("/Users/paulo.barenco/Desktop/Desktop_stuff/MyProject/embryonic/analysis/2_clustering/clustering/clustering_kmeans_umap.png")
for (i in files){ cat("![](",i,")") }
```


